Textmining in Economics

### 2017-10-18 paper/doc/doc.tex
intro

@@

die öffentlich-rechtlichen Anbieter sollten nur da auftreten, wo das privatwirtschaftliche Angebot klare Defizite aufweist.

>>>>

The debate about the role of public media and their mission in a rapidly changing media world is a recurring theme. If the right to use digital media were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision. They also threatened to lose their competitiveness with commercial media. But it is precisely this competitiveness that is constitutionally guaranteed. On the other hand, there is the concern of commercial providers who are registering an ever-increasing number of digital services financed by fees. They complain about a bias in competition caused by public media offering online text-content because of their fee financing. The regulator recognizes this inequality and has banned advertising and sponsorship in its online services.

The fundamental question in this debate is whether the offer of public news on the internet is justified. They should only occur where there are clear deficits in private sector supply. A frequently cited argument is that only the public media make it possible to provide information that is free of self-interest. Due to their public mandate and financing, they can afford what private providers cannot or only to a limited extent because of their economic dependency: a journalistic and editorial self-observation of society in the public interest. Due to their constitutional determination, they are obliged to the diversity and representation of the political and social spectrum of opinion in its entire breadth, including minority positions.

@@
